---
title: "ip_yzhao28"
output: html_document
---
```{r}
library(lpSolveAPI)
sp <- read.lp("ip_yzhao28.lp")
sp
```

```{r}
solve(sp)
get.objective(sp)
sp
```
```{r}
get.variables(sp)
sp
get.constraints(sp)
```
###remarks
We have already got x1= 3.75, and x2= 2.25, then we need to add more constraints to find integer solutions. 

###Branch 1
```{r}
sp1 <- read.lp("ip_1yzhao28.lp")
sp1 
```
```{r}
solve(sp1)
get.objective(sp1)
sp1
```

```{r}
get.variables(sp1)
sp1
get.constraints(sp1)
```
###remarks
We get the maximum is 39, and x1= 3, x2= 3. 

###Branch 2
```{r}
sp2 <- read.lp("ip_2yzhao28.lp")
sp2
```
```{r}
solve(sp2)
get.objective(sp2)
sp2
```
```{r}
get.variables(sp2)
sp2
get.constraints(sp2)
```
###remarks
we have got max= 41, and x1= 4, x2= 1.8.

###Branch3
```{r}
sp3 <- read.lp("ip_3yzhao28.lp")
sp3
```
```{r}
solve(sp3)
get.objective(sp3)
sp3
get.variables(sp3)
sp3
get.constraints(sp3)
```

###remarks 
we have got the max= 40.55556, x1= 4.444444, x2= 1. 

###Branch 4
```{r}
sp4 <- read.lp("ip_4yzhao28.lp")
sp4 
```

```{r}
solve(sp4)
get.objective(sp4)
sp4
get.variables(sp4)
sp4
get.constraints(sp4)
```
###remarks
We have got max= 37, x1= 4, x2= 1.

###Branch 5
```{r}
sp5 <- read.lp("ip_5yzhao28.lp")
sp5
```

```{r}
solve(sp5)
get.objective(sp5)
sp5
get.variables(sp5)
sp5
get.constraints(sp5)
```
###remarks
We have got max= 40, x1= 5, x2= 0.

###Branch 6
```{r}
sp6 <- read.lp("ip_6yzhao28.lp")
sp6
```
```{r}
solve(sp6)
get.objective(sp6)
sp6
get.variables(sp6)
sp6
get.constraints(sp6)
```
###remarks
No solution for this branch. 

###Branch 7
```{r}
sp7 <- read.lp("ip_7yzhao28.lp")
sp7
```
```{r}
solve(sp7)
get.objective(sp7)
sp7
get.variables(sp7)
sp7
get.constraints(sp7)
```
###remark
We have got max= 41.11111, and x1= 3.888889, x2= 2.

###Branch 8
```{r}
sp8 <- read.lp("ip_8yzhao28.lp")
sp8
```
```{r}
solve(sp8)
get.objective(sp8)
sp8
get.variables(sp8)
sp8
get.constraints(sp8)
```
###remarks
We have got max= 34, x1= 3, x2= 2. But 34 is smaller than 40. 

###Branch 9
```{r}
sp9 <- read.lp("ip_9yzhao28.lp")
sp9
```
```{r}
solve(sp9)
get.objective(sp9)
sp9
get.variables(sp9)
sp9
get.constraints(sp9)
```
###remarks
We have got max= 41, and x1= 4, x2= 1.8. 

###Branch 10
```{r}
sp10 <- read.lp("ip_10yzhao28.lp")
sp10
```
```{r}
solve(sp10)
get.objective(sp10)
sp10
get.variables(sp10)
sp10
get.constraints(sp10)
```
###remarks
We have got max= 40.55556, and x1= 4.444444, x2= 1. 

###Branch 11
```{r}
sp11 <- read.lp("ip_11yzhao28.lp")
sp11
```
```{r}
solve(sp11)
get.objective(sp11)
sp11
get.variables(sp11)
sp11
get.constraints(sp11)
```
###remarks
We have got max= 37, and x1= 4, x2= 1. 

###Branch 12
```{r}
sp12 <- read.lp("ip_12yzhao28.lp")
sp12
```
```{r}
solve(sp12)
get.objective(sp12)
sp12
get.variables(sp12)
sp12
get.constraints(sp12)
```
###remarks
We have got max= 40, and x1= 5, x2= 0. 

###Branch 13
```{r}
sp13 <- read.lp("ip_13yzhao28.lp")
sp13
```
```{r}
solve(sp13)
get.objective(sp13)
sp13
get.variables(sp13)
sp13
get.constraints(sp13)
```
###remarks
No solution for this branch.

###Branch 14
```{r}
sp14 <- read.lp("ip_14yzhao28.lp")
sp14
```
```{r}
solve(sp14)
get.objective(sp14)
sp14
get.variables(sp14)
sp14
get.constraints(sp14)
```
###remarks
We have got max= 39, and x1= 3, x2= 3. 

###remarks
I have put all variables into a csv file.

###Read
```{r}
variable <- read.csv("ip_yzhao28.csv")
variable
```
```{r}
summary(variable)
```

```{r}
library(ggplot2)
library(esquisse)
library(shiny)
```

```{r}
ggplot(data = variable) +
  aes(x = x1, y = x2) +
  geom_point(color = '#0c4c8a') +
  theme_minimal()
```
```{r}
ggplot(data = variable) +
  aes(x = Branch.., y = objective) +
  geom_line(color = '#0c4c8a') +
  theme_minimal()
```
###remarks
From this two graphs we can get the optimum solution for interger solutions. 
